---
title: My Penguins Report!
author: David Keyes
format: html
execute: 
  echo: false
  warning: false
  message: false
---

```{r}
library(tidyverse)
library(scales)

penguins <- read_csv("penguins.csv")
```

### Funders

1.  The **International** Society of Penguin Enthusiasts and Waddle Admirers
2.  The Coalition of People Who Are Definitely Not Anti-Penguin
3.  The International Coalition for the Appreciation and Ethical Treatment of Penguins

They are **very** excited about this report and they *really* hope you are too.

# Introduction

This report is about **three** species of penguins

1.  Adele
2.  Gentoo
3.  Chinstrap

You'll learn *so* much about the penguins. I hope you're ready!

## Results

Here is a chart showing the average bill length for penguins, grouped by island and sex.

```{r}
penguin_bill_length_by_island_and_sex <-
  penguins |>
  drop_na(sex) |>
  group_by(island, sex) |>
  summarize(mean_bill_length = mean(bill_length_mm))

ggplot(
  data = penguin_bill_length_by_island_and_sex,
  mapping = aes(
    x = island,
    y = mean_bill_length,
    fill = sex
  )
) +
  geom_col(position = "dodge")
```


```{r}
penguin_bill_length_by_island <-
  penguins |>
  group_by(island) |>
  summarize(mean_bill_length = mean(bill_length_mm, na.rm = TRUE)) |>
  arrange(mean_bill_length)

penguin_bill_length_by_island_v2 <-
  penguin_bill_length_by_island |>
  mutate(
    mean_bill_length_one_digit = number(
      mean_bill_length,
      accuracy = 0.1
    )
  )

ggplot(
  data = penguin_bill_length_by_island_v2,
  mapping = aes(
    x = island,
    y = mean_bill_length_one_digit,
    fill = island,
    label = mean_bill_length_one_digit
  )
) +
  geom_col() +
  geom_text()
```