---
title: My Penguins Report!
author: David Keyes
format: html
execute: 
  echo: false
  warning: false
  message: false
---

```{r}
library(tidyverse)

penguins <- read_csv("penguins.csv")
```

# Funders

1. The International Society of Penguin Enthusiasts and Waddle Admirers	
1. The Coalition of People Who Are Definitely Not Anti-Penguin
1. The International Coalition for the Appreciation and Ethical Treatment of Penguins
 
They are **very** excited about this report and they *really* hope you are too.

# Introduction

This report is about **three** species of penguins

1. Adele
1. Gentoo
1. Chinstrap

You'll learn *so* much about the penguins. I hope you're ready!

## Results

Here is a chart showing the average bill length for penguins, grouped by island and sex.

```{r}
penguin_bill_length_by_island_and_sex <-
  penguins |>
  drop_na(sex) |>
  group_by(island, sex) |>
  summarize(mean_bill_length = mean(bill_length_mm))

ggplot(
  data = penguin_bill_length_by_island_and_sex,
  mapping = aes(
    x = island,
    y = mean_bill_length,
    fill = sex
  )
) +
  geom_col(position = "dodge")
```